\section{Benefits}
The biggest benefit of Continous Integration is reduced risk. Long and big projects are hard to oversee. With Continous Integration there is no long integration.
There is no blind spot where you don't know how long it will take to get a working build. At all time you know what works and what does not.
You always know when a Bug appears and when it disappears. Bugs hinder your progress and with Continous Integration they are more managable.
Of course with Continous Integration alone you will not magically get rid of all bugs. It just makes them a lot easier to find. Because there are only small changes 
to check, bugs are far more fixable. Also that changed code is just fresh in memory of the developer, so the fix should be easier to find.
It prevents the cumulation of multiple bugs, which make a single bug even harder to fix.\footnote{\url{http://www.martinfowler.com/articles/continuousIntegration.html}}

There are more benefits, just to name a few: \footnote{\url{https://blog.codeship.com/benefits-of-continuous-integration/}}
\begin{itemize}
\item Eradication of manual FTP deployment
\item Prevention \& reduction of production \& staging errors
\item Generation of analysis \& reporting on the health of the code base
\end{itemize}

In business terms, the value of Continuous Integration is:
\begin{itemize}
\item Reducing risk
\item Reducing overheads across the development \& deployment process
\item Enhancing the reputation of the company by providing Quality Assurance
\end{itemize}


